Nested sampling with two or more objective functions

### 2015-10-25 Paper/ms.tex
refer to figure

The corner count of particle $i$ is defined as the number of particles with
a lower value of {\em both} objective functions compared to particle $i$.
Graphically, on a plot of $L_2$ vs. $L_1$ the corner count is the number of
particles in the rectangle whose upper right corner is at
$\left(L_1(\xx_i), L_2(\xx_i)\right)$. The equation for the corner count is:
\begin{eqnarray}
C_i &=& \sum_{j=1}^N \mathds{1}\left(L_1(\xx_j) < L_1(\xx_i),
L_2(\xx_j) < L_2(\xx_i)
\right).\label{eqn:corner_count}
\end{eqnarray}

>>>>

The corner count of particle $i$ is defined as the number of particles with
a lower value of {\em both} objective functions compared to particle $i$.
Graphically, on a plot of $L_2$ vs. $L_1$ the corner count is the number of
particles in the rectangle whose upper right corner is at
$\left(L_1(\xx_i), L_2(\xx_i)\right)$ (see Figure~\ref{fig:joint} for an
example). The equation for the corner count is:
\begin{eqnarray}
C_i &=& \sum_{j=1}^N \mathds{1}\left(L_1(\xx_j) < L_1(\xx_i),
L_2(\xx_j) < L_2(\xx_i)
\right).\label{eqn:corner_count}
\end{eqnarray}
